\documentclass[]{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}

%opening
\title{Formalizing Fuzzy DL with DNN}
\author{Tilman Hinnerichs, Robert Hoehndorf}
\date{}

\begin{document}

\maketitle

\section{Definitions}

Given this ontology (mainly interested in T-box) (for now only consider EL++), we want to do perform reasoning and eventually proof soundness, correctness, completeness. 

Input: Some Ontology
\begin{align*}
	\mathcal{O}&=(\Sigma,\mathcal{T,A})\\
	\Sigma &=(\mathbf{C,R,I})\\
	\mathcal{T} &= \mathcal{T}_{NF1} \cup \mathcal{T}_{NF2} \cup \mathcal{T}_{NF3} \cup \mathcal{T}_{NF4}\\
	\mathcal{A}&=\{a:C\} \cup \{ R(x,y) | ... \}
\end{align*}

\begin{enumerate}
	\item Optional: A Box elimination:
	\begin{align*}
		\mathbf{C'}:=& \mathbf{C} \cup \mathbf{I}\\
		\mathcal{T}':=& \mathcal{T} \cup\{\{a\}\sqsubseteq\exists r.\{b\}|\forall r(a,b)\in \mathcal{A}\}\\
		&\cup \{\{a\}\sqsubseteq C| \forall (a:C)\in\mathcal{A}\}\\
		(\mathcal{A}':=&\emptyset)
	\end{align*}

        \item Explicit description of Fuzzy Semantics for DL
        \item distinction of $f_{embed}$ and $f_{fuzz}$; choice of
          parameters ($n$, $m$)
        \item characterization of model theory: assumption of UNA and
          DCA vs non-DCA semantics (and non-UNA)
        \item infinite domain of discourse ($\Delta^\omega$) as most
          general case due to (a) existence of infinite models and (b)
          Loewenheim-Skolem (downwards); describe combination of
          $f_{embed}$ and $f_{fuzz}$ to generate (fuzzy)
          interpretations for all formulas; potentially use projection
          relations for relations;
        \item investigation of limiting $\omega$ to finite subsets
        \item describe which operations are suitable in latent space
          and which explicit on fuzzy sets
        
      % \item Potentially: Add new individuals for each concept:
      %   \begin{align*}
      %     \mathbf{I'}&:=\{c_C | C\in\mathbf{C'}\}\\
      %   \end{align*}
      %   Not necessary --- but way to get ``witnesses'' based on which
      %   we represent fuzzy extensions\\
      %   needs some thought on ``unsatisfiable'' concepts

      \item Introduce mappings/functions (learnable neural nets) (see \cite{LTN}).\\
	We basically embed all individuals into $\mathbb{R}^n$, and train neural nets to decide and describe fuzzy affiliation to concept. $n$ is dimensionality of latent space and thus a hyperparameter.
	\begin{itemize}
		\item $f_{emb}:\mathbf{C}\cup \mathbf{I}\rightarrow\mathbb{R}^n$ : Mapping all individuals into latent space
		\item $f_{skol}:\mathbb{R}^n\rightarrow\mathbb{R}^n$ : Skolemizing function, as we only consider EL++ only relevant for normal forms $C\sqsubseteq\exists R.D$ and $\exists R.C\sqsubseteq D$. We make $f_{skol}(c_C)$ dependent on both $f_{emb}(c_D)$ and the relation $R$, which should suffice through axiomatization theorem?
		\item $f_{class}:\mathbb{R}^n\rightarrow [0,1]^{|C'|}$: describes for all points in $\mathbb{R}^n$ its fuzzy association with each concept:
		\begin{equation*}
			C^\mathcal{I}(c_C)=(f_{class} \circ f_{emb})(c_C)
		\end{equation*}
	\end{itemize}
	\item Maximize satisfaction of all axioms over all individuals (we only care about $\mathbf{I}$, e.g. given $C\sqsubseteq D\in \mathcal{T}$ we want to find above functions such that
	\begin{equation}
		\max (C^\mathcal{I} \rightarrow D^\mathcal{I})(d) = \rightarrow (C^\mathcal{I}(d), D^\mathcal{I}(d))
	\end{equation}
	with fuzzy implication $\rightarrow:[0,1] \times [0,1]\rightarrow [0,1]$
	
\end{enumerate}
We basically follow \cite{LTN}, but do not solve quantification over grounding, but over skolemization for $\exists$. Finiteness would be cool in order to compute satisfaction of $\forall$ 

Questions for Tobias:
\begin{itemize}
	\item This should have an infinite Herbrand universe as model?
	\item is the skolemization correct? Does it yield feasible fresh elements?
	\item Are there finite models? One model could be subsets of $\mathbb{R}^n$ (crisp fuzzy sets $A_{\geq t}$ with global threshold $t$) and $\sqsubset = \subseteq$, but then skolemization will not yield fresh elements of domain
	\item correctness: This should be correct as for $ loss = 1-satisfaction = 0$ this is crisp, and hence this is a model of underlying EL++ instance
\end{itemize}



\section{Questions to answer}

\begin{itemize}
	\item Proper definitions?
	\item infinite universe? If so what is the issue?
	\item can we just take finite subset of universe?
  \item decidability and completeness
\end{itemize}




\begin{itemize}
	\item what are the individuals actually?
	\item formalize the three functions
	\item What are the mappings meaning?
	\begin{itemize}
		\item embedding function
		\item Skolemizer
		\item fuzzy set descriptor
	\end{itemize}
	\item What is the actual knowledge base? 
	
\end{itemize}


\begin{thebibliography}{100}
	\bibitem[LTN]{LTN} \url{https://arxiv.org/abs/2012.13635}
\end{thebibliography}




\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
